Weak interspecific interactions in a sagebrush steppe\new{? Conflicting evidence from observations and experiments}

### 2018-03-02 removals/manuscript/removal_ms.tex
Reformatted figure legends

\usepackage{amsmath,amsfonts,amssymb,graphicx,setspace,authblk}
\usepackage{float}
\usepackage[running]{lineno}
\usepackage[vmargin=1in,hmargin=1in]{geometry}

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=1\textwidth]{treatment_trends_cover}
\caption{Cover trends by treatment for the four dominant species.  Note the difference in y-axis scale between the canopy cover of \textit{A. tripartita} and 
the basal cover of the dominant grasses. ``Shrub removal'' refers to removal of \textit{A. tripartita}, and ``Grass removal'' refers to removal of all perennial grasses. 
The cover of species in treatments from which they are removed (e.g. \textit{A. tripartita} cover in shrub removal plots) is included to show values at the start 
of the experiment in 2011 and the efficacy of the removal treatments. Source file: \texttt{treatment\textunderscore trends\textunderscore removals.r}.}
\label{fig:CoverTrends}
\end{figure}

@@

 \begin{figure}[tbp]
 \centering
 \includegraphics[width=1\textwidth]{treatment_tests}
 \caption{Effects of removal treatments on the survival, growth, and recruitment of the four dominant species. Circles show the estimated coefficient of the removal effect, bars show 95\% credible intervals. The removal effect shows response of \textit{A. tripartita} (``ARTR") to perennial grass removal, and response of the perennial grasses to \textit{A. tripartita} removal, after accounting for local neighborhood interactions. The other species codes are HECO: \textit{Hesperostipa comata}, POSE: \textit{Poa secunda}, and PSSP: \textit{Pseudoroegneria spicata}.
 Source file: \texttt{treatment\textunderscore test\textunderscore figure.r}.}
 \label{fig:VitalRateTest}
 \end{figure}

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=1\textwidth]{growth_residuals_vs_quad_removal_cover}
\caption{The relationship between residuals from the fitted growth model and quadrat-level pre-treatment cover of the removal species (all grasses removed in quadrats where we studied \textit{A. tripartita}, and \textit{A. tripartita} removed in the quadrats where we studied the grasses). Linear regressions are shown only when statistically significant. Source file:  \texttt{growth\textbackslash growth\textunderscore residuals\textunderscore by\textunderscore quad.R}.}
\label{fig:GrowthResidsQuad}
\end{figure}

@@

 \begin{figure}[tbp]
 \centering
 \includegraphics[width=1\textwidth]{obsVpred_quad_year}
 \caption{The relationship between observed and predicted cover for each quadrat, year, and species. The 1:1 line is dashed, the solid black line shows the trend for control plots with predictions from the baseline IBM model (black symbols), the blue line shows the trend for removal plots with predictions from the baseline model (blue symbols), and the red line shows the trend for removal plots with predictions from the removal model (red symbols). Source file: \texttt{ibm\textbackslash summarize\textunderscore sims1step.r}. }
 \label{fig:obsVpred}
 \end{figure}

@@

 \begin{figure}[tbp]
 \centering
 \includegraphics[width=1\textwidth]{cover_projections_1step}
 \caption{Observed and predicted cover for each of the four modeled species. Solid black lines show mean observed cover averaged across control (closed symbols) and removal treatment (open symbols) quadrats. Blue lines and symbols show one-step-ahead predictions from the baseline IBM (no removal treatment coefficients), averaged across quadrats. Red lines and symbols show one-step-ahead predictions from an IBM that includes removal treatment coefficients. For \textit{H. comata}, lines showing predictions for the baseline and removal effect models are virtually indistinguishable. Source file: \texttt{ibm\textbackslash summarize\textunderscore sims1step.r}. }
 \label{fig:IBM1step}
 \end{figure}

@@

 \begin{figure}[tbp]
 \centering
 \includegraphics[width=1\textwidth]{boxplots}
 \caption{Equilibrium cover of the four dominant species simulated by the IPM. Boxplots show interannual variation reflecting random year effects. Gray boxes show cover simulated by a model with \textit{A. tripartita} present and no removal treatment coefficients, blue boxes show results from the same model but with \textit{A. tripartita} cover set to zero (a species removal), and red boxes show results from a model with \textit{A. tripartita} set to zero and removal treatment coefficients included. Source file: \texttt{ipm\textbackslash IPM-figures.r}.}
 \label{fig:IPMresults}
 \end{figure}

@@

>>>>

\usepackage{amsmath,amsfonts,amssymb,graphicx,setspace,authblk}
\usepackage{float}
\usepackage[running]{lineno}
\usepackage[vmargin=1in,hmargin=1in]{geometry}
\usepackage{caption}

@@

@@

@@

@@

@@

@@

@@

\newpage
\section*{Figure legends}

\textbf{Figure 1.} Cover trends by treatment for the four dominant species.  Note the difference in y-axis scale between the canopy cover of \textit{A. tripartita} and the basal cover of the dominant grasses. ``Shrub removal'' refers to removal of \textit{A. tripartita}, and ``Grass removal'' refers to removal of all perennial grasses. The cover of species in treatments from which they are removed (e.g. \textit{A. tripartita} cover in shrub removal plots) is included to show values at the start of the experiment in 2011 and the efficacy of the removal treatments. Source file: \texttt{treatment\textunderscore trends\textunderscore removals.r}

\vspace{3mm}

\noindent \textbf{Figure 2.} Effects of removal treatments on the survival, growth, and recruitment of the four dominant species. Circles show the estimated coefficient of the removal effect, bars show 95\% credible intervals. The removal effect shows response of \textit{A. tripartita} (``ARTR") to perennial grass removal, and response of the perennial grasses to \textit{A. tripartita} removal, after accounting for local neighborhood interactions. The other species codes are HECO: \textit{Hesperostipa comata}, POSE: \textit{Poa secunda}, and PSSP: \textit{Pseudoroegneria spicata}.
 Source file: \texttt{treatment\textunderscore test\textunderscore figure.r}.

 \vspace{3mm}

\noindent \textbf{Figure 3.} The relationship between residuals from the fitted growth model and quadrat-level pre-treatment cover of the removal species (all grasses removed in quadrats where we studied \textit{A. tripartita}, and \textit{A. tripartita} removed in the quadrats where we studied the grasses). Linear regressions are shown only when statistically significant. Source file:  \texttt{growth\textbackslash growth\textunderscore residuals\textunderscore by\textunderscore quad.R}.

\vspace{3mm}

\noindent \textbf{Figure 4.} The relationship between observed and predicted cover for each quadrat, year, and species. The 1:1 line is dashed, the solid black line shows the trend for control plots with predictions from the baseline IBM model (black symbols), the blue line shows the trend for removal plots with predictions from the baseline model (blue symbols), and the red line shows the trend for removal plots with predictions from the removal model (red symbols). Source file: \texttt{ibm\textbackslash summarize\textunderscore sims1step.r}.

\vspace{3mm}

\noindent \textbf{Figure 5.} Observed and predicted cover for each of the four modeled species. Solid black lines show mean observed cover averaged across control (closed symbols) and removal treatment (open symbols) quadrats. Blue lines and symbols show one-step-ahead predictions from the baseline IBM (no removal treatment coefficients), averaged across quadrats. Red lines and symbols show one-step-ahead predictions from an IBM that includes removal treatment coefficients. For \textit{H. comata}, lines showing predictions for the baseline and removal effect models are virtually indistinguishable. Source file: \texttt{ibm\textbackslash summarize\textunderscore sims1step.r}.

\vspace{3mm}

 \noindent\textbf{Figure 6.} Equilibrium cover of the four dominant species simulated by the IPM. Boxplots show interannual variation reflecting random year effects. Gray boxes show cover simulated by a model with \textit{A. tripartita} present and no removal treatment coefficients, blue boxes show results from the same model but with \textit{A. tripartita} cover set to zero (a species removal), and red boxes show results from a model with \textit{A. tripartita} set to zero and removal treatment coefficients included. Source file: \texttt{ipm\textbackslash IPM-figures.r}

\captionsetup[figure]{labelfont=bf, labelsep=none, justification=raggedright,singlelinecheck=false}

\clearpage
\begin{figure}[tbp]
\centering
\includegraphics[width=1\textwidth]{treatment_trends_cover}
\caption{}
\label{fig:CoverTrends}
\end{figure}

\clearpage
 \begin{figure}[tbp]
 \centering
 \includegraphics[width=1\textwidth]{treatment_tests}
 \caption{}
 \label{fig:VitalRateTest}
 \end{figure}

 \clearpage
 \begin{figure}[tbp]
 \centering
 \includegraphics[width=1\textwidth]{growth_residuals_vs_quad_removal_cover}
 \caption{}
 \label{fig:GrowthResidsQuad}
 \end{figure}

 \clearpage
  \begin{figure}[tbp]
  \centering
  \includegraphics[width=1\textwidth]{obsVpred_quad_year}
  \caption{}
  \label{fig:obsVpred}
  \end{figure}

  \clearpage
   \begin{figure}[tbp]
   \centering
   \includegraphics[width=1\textwidth]{cover_projections_1step}
   \caption{}
   \label{fig:IBM1step}
   \end{figure}

   \clearpage
    \begin{figure}[tbp]
    \centering
    \includegraphics[width=1\textwidth]{boxplots}
    \caption{}
    \label{fig:IPMresults}
    \end{figure}
